### 2023-02-08 paper-thesis/chapters/10-coc.tex
More feedback processed

\begin{lstlisting}
sPutType  : scope * ID * Expr -> scope
sPutSubst : scope * ID * (scope * Expr) -> scope
sGetName  : scope * ID -> NameEntry
sEmpty    : -> scope
\end{lstlisting}
The \verb|sPutType| and \verb|sPutSubst| predicates generate a new scope given a parent scope and a type or a substitution respectively. These return a scope that represent an environment that has been extended with the new name. To query the scope graph we use \verb|sGetName|, which will return the closest \verb|NameEntry| with a matching name. Finally, \verb|sEmpty| returns a fresh empty scope.

We will define a \emph{scoped expression}, as a pair of a scope and an expression. The scope acts as the environment of the expression, containing all of the context needed to evaluate the expression.

@@

We need to define multiple predicates that will be used later for type checking. First, the primary predicate is \verb|betaReduceHead|, that takes a scoped expression and a stack of applications, and returns a head-normal expression. The scope acts as the environment from~\cite{krivine}, using \verb|NSubst| to store substitutions. All rules for \verb|betaReduceHead| are given in figure \ref{fig:beta-head-reduce-rules}. We use the syntax $\bhr{\scope{s_1}{e_1}}{\overline{p}}{\scope{s_2}{e_2}}$ to express \verb|betaReduceHead((s1, e1), ps) == (s2, e2)|. The $\overline{p}$ in this definition is the argument stack of the Krivine machine. The argument stack is a stack of scoped expressions, which are the arguments that are not yet paired with a matching function. Figure \ref{fig:beta-head-reduce-rules} contains the rules necessary for beta head reduction of the language. One predicate that is used for this is the \verb|rebuild| predicate, which takes a scoped expression and the stack of arguments (of the Krivine machine state) and converts it to an expression by adding \verb|FnDestruct|s. Its signature is:
\begin{lstlisting}
rebuild : (scope * Expr) * list((scope * Expr)) -> (scope * Expr)
\end{lstlisting}

@@

\begin{lstlisting}
typeOfExpr : scope * Expr -> Expr
\end{lstlisting}
We can then start defining type checking rules for the language. We introduce a number of judgements for typing and equality together with their counterparts in Statix.
\begin{enumerate}
	\item $\toe{s}{e}{t}$ is the same as \verb|typeOfExpr(s, e) == t|
	\item $\beq{\scope{s1}{e1}}{\scope{s2}{e2}}$ is the same as \verb|expectBetaEq((s1, e1), (s2, e2))|
	\item $\bhr{\scope{s1}{e1}}{\overline{p}}{\scope{s2}{e2}}$ is the same as \verb|betaReduceHead((s1, e1), ps) == (s2, e2)| \\ (The same as in section \ref{sec:coc-dynsyms})
	\item $\bred{s1}{e1}{e2}$ is the same as \verb|betaReduce((s1, e1)) == e2|
	\item $\scope{sEmpty}{e}$ is the same as $e$ (empty scopes can be left out)
\end{enumerate}

>>>>

\begin{lstlisting}
sPutType  : scope * ID * Expr -> scope
sPutSubst : scope * ID * (scope * Expr) -> scope
sGetName  : scope * ID -> NameEntry
sEmpty    : -> scope
\end{lstlisting}
The \verb|sPutType| and \verb|sPutSubst| predicates generate a new scope given a parent scope and a type or a substitution respectively. These return a scope that represent an environment that has been extended with the new name. To query the scope graph, we use \verb|sGetName|, which will return the closest \verb|NameEntry| with a matching name. Finally, \verb|sEmpty| returns a fresh empty scope.

We define a \emph{scoped expression}, as a pair of a scope and an expression. The scope acts as the environment of the expression, containing all of the context needed to evaluate the expression.

@@

We need to define multiple predicates that will be used later for type checking. First, the primary predicate is \verb|betaReduceHead|, that takes a scoped expression and a stack of applications, and returns a head-normal expression. The scope acts as the environment from~\cite{krivine}, using \verb|NSubst| to store substitutions. All rules for \verb|betaReduceHead| are given in figure \ref{fig:beta-head-reduce-rules}. We use the syntax $\bhr{\scope{s_1}{e_1}}{\overline{p}}{\scope{s_2}{e_2}}$ to express \textit{betaReduceHead((s1, e1), ps) == (s2, e2)}. The $\overline{p}$ in this definition is the argument stack of the Krivine machine. The argument stack is a stack of scoped expressions, which are the arguments that are not yet paired with a matching function. Figure \ref{fig:beta-head-reduce-rules} contains the rules necessary for beta head reduction of the language. One predicate that is used for this is the \verb|rebuild| predicate, which takes a scoped expression and the stack of arguments (of the Krivine machine state) and converts it to an expression by adding \verb|FnDestruct|s. Its signature is:
\begin{lstlisting}
rebuild : (scope * Expr) * list((scope * Expr)) -> (scope * Expr)
\end{lstlisting}

@@

\begin{lstlisting}
typeOfExpr : scope * Expr -> Expr
\end{lstlisting}
We can then start defining type checking rules for the language. We introduce a number of judgements for typing and equality together with their counterparts in Statix.
\begin{enumerate}
	\item $\toe{s}{e}{t}$ is the same as \verb|typeOfExpr(s, e) == t|
	\item $\beq{\scope{s_1}{e_1}}{\scope{s_2}{e_2}}$ is the same as \verb|expectBetaEq((s1, e1), (s2, e2))|
	\item $\bhr{\scope{s_1}{e_1}}{\overline{p}}{\scope{s_2}{e_2}}$ is the same as \verb|betaReduceHead((s1, e1), ps) == (s2, e2)| \\ (The same as in section \ref{sec:coc-dynsyms})
	\item $\bred{s_1}{e_1}{e_2}$ is the same as \verb|betaReduce((s1, e1)) == e2|
	\item $\scope{\co{sEmpty}}{e}$ is the same as $e$ (empty scopes can be left out)
\end{enumerate}
